---
title: "Tidyverse Exercises"
tutorial:
  id: "com.sagrsoft.tutorials.tidyverseex"
  version: 0.01
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: Practice tidyverse exercises to jog your memory.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)

che <- function(
  label,
  user_code,
  solution_code,
  check_code,
  envir_result,
  evaluate_result,
  envir_prep,
  ...
) {
  if (trimws(user_code) == trimws(solution_code)) {
    list(message = "Great Job!", correct = TRUE, location = "append")  
  }
  else {
    list(message = "Incorrect Answer!", correct = FALSE, location = "append")
  }
}

knitr::opts_chunk$set(echo = FALSE, exercise.checker = che)

iris <- tibble(iris)
```


## Tibble

For the following exercises we're going to use the iris data set that comes with R. It was changed from data frame to tibble with the code: 
`iris <- tibble(iris)`.  All work done in exercises don't save the changes made to the iris data set from exercise to exercise.

### Exercise 1/7

Write the R code required to see the iris tibble transposed (used for seeing all column names in tibble when you have a lot):

```{r glimpse, exercise=TRUE}

```

```{r glimpse-solution}
glimpse(iris)
```

```{r glimpse-check}
TRUE
```

### Exercise 2/7

Write the R code required to add a column of 1's named Height after column Sepal.Width using the pipe operator.

```{r addcol, exercise=TRUE}

```

```{r addcol-solution}
iris %>% 
  add_column(Height = 1, .after = "Sepal.Width")
```

```{r addcol-check}
TRUE
```

### Exercise 3/7

Write the R code required to add a row in position 2 with Sepal.Length = 2, Sepal.Width = 1, Species = as_factor("setosa") and the rest of the unspecified columns equal NA. 

```{r addrow, exercise=TRUE}

```

```{r addrow-solution}
iris %>% 
  add_row(Sepal.Width = 1, Sepal.Length = 2, Species = as_factor("setosa"), .before = 2)
```

```{r addrow-check}
TRUE
```

### Exercise 4/7

From an unnamed atomic vector with values from 1 to 10 create a tibble with only one column named "Numbers" with these values. 

```{r enframe1, exercise=TRUE}

```

```{r enframe1-solution}
enframe(x = 1:10, name = NULL, value = "Numbers")
```

```{r enframe1-check}
TRUE
```

### Exercise 5/7

From a named atomic vector with values from 1 to 3 and names from a to c create a tibble with two columns named "Names" and "Numbers" with these values. 

```{r enframe2, exercise=TRUE}

```

```{r enframe2-solution}
enframe(x = c(a = 1, b = 2, c = 3), name = "Names", value = "Numbers")
```

```{r enframe2-check}
TRUE
```

### Exercise 6/7

From the following tibble named pop change it to a named vector.

```{r deframet}
(pop <- tibble(city = c("San Francisco", "Los Angeles", "New York"),
              population = c(900022, 4040000, 8700000)))
```

```{r deframe, exercise=TRUE}

```

```{r deframe-solution}
deframe(pop)
```

```{r deframe-check}
TRUE
```

### Exercise 7/7

Create a tibble from a row-by-row layout.  Column names should be "Letters" and "Numbers".  First row has values "a", 1; second row has values "b", 2; third row has values "c", 3.

```{r tribble, exercise=TRUE}

```

```{r tribble-solution}
tribble(~Letters, ~Numbers,
        "a",   1,
        "b",   2,
        "c",   3)
```

```{r tribble-check}
TRUE
```

## Readr

### Exercise

## Dplyr

### Exercise
