---
title: "Tidyverse Exercises"
tutorial:
  id: "com.sagrsoft.tutorials.tidyverseex"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: Practice tidyverse exercises to jog your memory.
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(BeTidy)

che <- function(
  label,
  user_code,
  solution_code,
  check_code,
  envir_result,
  evaluate_result,
  envir_prep,
  ...
) {
  if (trimws(user_code) == trimws(solution_code)) {
    list(message = "Great Job!", correct = TRUE, location = "append")  
  }
  else {
    list(message = "Incorrect Answer!", correct = FALSE, location = "append")
  }
}

knitr::opts_chunk$set(echo = FALSE, exercise.checker = che)

iris <- tibble(iris)
```


## Tibble

For the following exercises we're going to use the iris data set that comes with R. It was changed from data frame to tibble with the code: 
`iris <- tibble(iris)`.  All work done in exercises don't save the changes made to the iris data set from exercise to exercise.

### Exercise 1/7

Write the R code required to see the iris tibble transposed (used for seeing all column names in tibble when you have a lot):

```{r glimpse, exercise=TRUE}

```

```{r glimpse-solution}
glimpse(iris)
```

```{r glimpse-check}
TRUE
```

### Exercise 2/7

Write the R code required to add a column of 1's named Height after column Sepal.Width using the pipe operator.

```{r addcol, exercise=TRUE}

```

```{r addcol-solution}
iris %>% 
  add_column(Height = 1, .after = "Sepal.Width")
```

```{r addcol-check}
TRUE
```

### Exercise 3/7

Write the R code required to add a row in position 2 with Sepal.Length = 2, Sepal.Width = 1, Species = as_factor("setosa") and the rest of the unspecified columns equal NA. 

```{r addrow, exercise=TRUE}

```

```{r addrow-solution}
iris %>% 
  add_row(Sepal.Width = 1, Sepal.Length = 2, Species = as_factor("setosa"), .before = 2)
```

```{r addrow-check}
TRUE
```

### Exercise 4/7

From an unnamed atomic vector with values from 1 to 10 create a tibble with only one column named "Numbers" with these values. 

```{r enframe1, exercise=TRUE}

```

```{r enframe1-solution}
enframe(x = 1:10, name = NULL, value = "Numbers")
```

```{r enframe1-check}
TRUE
```

### Exercise 5/7

From a named atomic vector with values from 1 to 3 and names from a to c create a tibble with two columns named "Names" and "Numbers" with these values. 

```{r enframe2, exercise=TRUE}

```

```{r enframe2-solution}
enframe(x = c(a = 1, b = 2, c = 3), name = "Names", value = "Numbers")
```

```{r enframe2-check}
TRUE
```

### Exercise 6/7

From the following tibble named pop change it to a named vector.

```{r deframet}
(pop <- tibble(city = c("San Francisco", "Los Angeles", "New York"),
              population = c(900022, 4040000, 8700000)))
```

```{r deframe, exercise=TRUE}

```

```{r deframe-solution}
deframe(pop)
```

```{r deframe-check}
TRUE
```

### Exercise 7/7

Create a tibble from a row-by-row layout.  Column names should be "Letters" and "Numbers".  First row has values "a", 1; second row has values "b", 2; third row has values "c", 3.

```{r tribble, exercise=TRUE}

```

```{r tribble-solution}
tribble(~Letters, ~Numbers,
        "a",   1,
        "b",   2,
        "c",   3)
```

```{r tribble-check}
TRUE
```

## Readr

For the following exercises we will be using an example population dataset.  You can use the helper functions included with BeTidy to get the path of each type of file. For example you can retrieve the path of the csv file with the function
example_csv_path().

### Exercise 1/6

Read from file the population csv file and save it into variable pop_csv, surround with parenthesis so that it prints.

```{r read_csv, exercise=TRUE}

```

```{r read_csv-solution}
(pop_csv <- read_csv(example_csv_path()))
```

```{r read_csv-check}
TRUE
```

### Exercise 2/6

Read from file the population csv file and save it into variable pop_csv, surround with parenthesis so that it prints. Read the Region column (1st) as factor and the Number column (2nd) as double, last column should be skipped. Use the abbreviation to specify column types.

```{r read_csv2, exercise=TRUE}

```

```{r read_csv2-solution}
(pop_csv <- read_csv(example_csv_path(), col_types = "fd_"))
```

```{r read_csv2-check}
TRUE
```

### Exercise 3/6

Read from file the population csv file and save it in variable popm as a melted tibble with one row for each token. Surround in parenthesis so that it prints.

```{r melt_csv, exercise=TRUE}

```

```{r melt_csv-solution}
(popm_csv <- melt_csv(example_csv_path()))
```

```{r melt_csv-check}
TRUE
```

### Exercise 4/6

Read from file the population tsv file and save it into variable pop_tsv, surround with parenthesis so that it prints.

```{r read_tsv, exercise=TRUE}

```

```{r read_tsv-solution}
(pop_tsv <- read_tsv(example_tsv_path()))
```

```{r read_tsv-check}
TRUE
```

### Exercise 5/6

Read from file the population delimited file and save it into variable pop_delim, surround with parenthesis so that it prints.  The file is delimited with ";".

```{r read_delim, exercise=TRUE}

```

```{r read_delim-solution}
(pop_delim <- read_delim(example_delim_path(), delim = ";"))
```

```{r read_delim-check}
TRUE
```

### Exercise 6/6

Read from file the population csv file and save it as a list of lines into variable pop_lines, surround with parenthesis so that it prints.  

```{r read_lines, exercise=TRUE}

```

```{r read_lines-solution}
(pop_lines <- read_lines(example_csv_path()))
```

```{r read_lines-check}
TRUE
```

From a tibble, you can create the different types of files with functions write_csv(), write_tsv(), write_delim(), write_lines(). There aren't example exercises so as to not pollute your workspace.

## Dplyr

### Exercise
